Microlensing as a possible probe of event-horizon structure in quasars

### 2016-07-20 paper1/ms.tex
figures improvement
editing

Active galactic nuclei are thought to be powered by the
accretion of matter from the proximal environment into a supermassive
black hole.  The radiation emitted excites the surrounding medium
which becomes detectable as narrow line regions, broad line regions
and optical continuum.  Moreover, in the direction perpendicular to
the accretion disc, where the medium is more transparent, jets will
appear.  If a jet is oriented towards the Earth, a quasar is observed
\citep[e.g.,][]{1984RvMP...56..255B}.  While the basic mechanism
\citep[originating in the work
  of][]{1964ApJ...140..796S,1964SPhD....9..246Z,1969Natur.223..690L}
is not in doubt, the central engines, near the event horizons of the
black holes, remain to be probed.

For the black holes in the Galactic centre and the centre of M87
---the two nearest objects that barely qualify as AGN--- the central
engines (which are $<0.1\rm\,mas$ on the sky) are close to being
resolved through very long baseline interferometry, which shows
preliminary indications of the jet-launching structures
\citep{2008JPhCS.131a2055D,2012Sci...338..355D,2013MNRAS.434..765K,2016arXiv160205527F}.
Current data do not deliver images but require fitting to
predefined models for the images.  A whole range of models have been
applied, starting from simple geometric models to more complex
physical models
\citep{2008Natur.455...78D,2011ApJ...738...38B,2009ApJ...706..497M,2010ApJ...717.1092D}.
The more complicated models nonetheless tend to predict a crescent
shaped silhouette of the black hole.  This motivated
\cite{2013MNRAS.434..765K} to use a simple geometric crescent model to
fit the data, and argued that the crescent is nothing but the
silhouette of the event horizon.

@@

\begin{figure}
\centering
  \includegraphics[width=0.9\hsize]{figures/cc_forward.eps}
\caption{\label{fig:cc_forward} Mock lightcurve fitted with the
  correct source type and caustic.  The upper panel shows the mock
  data points, and running through them is a seven-parameter best fit:
  these being the crescent parameters $(R_p,R_n,a,b)$ and additionally
  the start and end times and the overall normalisation.  (Ideal
  lightcurves for the same crescent parameters appear above in
  Figures~\ref{fig:lightcurve_gauss}, \ref{fig:lightcurve_disk},
  \ref{fig:lightcurve_crescent} and \ref{fig:char_points}.)  The curve
  has $\chi^2=243, P=0.32$ indicating a good fit.  The lower panel
  shows the posterior distributions for $r_{1/2}$ (solid histogram)
  and $R_n/R_p$ (dashed histogram).}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=0.9\hsize]{figures/cc_backward.eps}
\caption{\label{fig:cc_backward} Like Figure~\ref{fig:cc_backward},
  except that the fit uses path~II whereas the mock data still come
  from path~I. The curve has $\chi^2=284, P=0.01$ indicating a
  marginally acceptable fit.}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=0.9\hsize]{figures/gc_forward.eps}
\caption{\label{fig:gc_forward} Like Figure~\ref{fig:cc_backward}, but
  showing the best fit to a Gaussian source.  The histogram shows the
  posterior distribution of $r_{1/2}$ (there is no $R_n$).  It appears
  to show $r_{1/2}$ as accurately recovered, but is not to be trusted,
  because the fit has $\chi^2=344, P=3\times10^{-6}$ indicating
  rejection of the Gaussian source.  Looking closely, the curve is a
  little too shallow near $t=3$, and it is unable to fit the second
  sub-peak near $t=5$.}
\end{figure}

>>>>

Active galactic nuclei are thought to be powered by the accretion of
matter from the proximal environment into a supermassive black hole.
The radiation emitted excites the surrounding medium which becomes
detectable as narrow line regions, broad line regions and optical
continuum.  In the direction perpendicular to the accretion disc,
where the medium is more transparent, the outflow tends to be
collimated to jets.  If the orientation is such that the observer's
view of the central region is not blocked by the accretion disc or by
a jet, a quasar is seen \citep[e.g.,][]{1984RvMP...56..255B}.  While
the basic mechanism \citep[originating in the work
  of][]{1964ApJ...140..796S,1964SPhD....9..246Z,1969Natur.223..690L}
is not in doubt, the central engines, near the event horizons of the
black holes, remain to be probed.

Modestly active galactic nucleii are present in the Galactic centre
and in M87.  In these two cases, the central engines ($<0.1\rm\,mas$
on the sky) are close to being resolved through very long baseline
interferometry, which shows preliminary indications of the
jet-launching structures
\citep{2008JPhCS.131a2055D,2012Sci...338..355D,2013MNRAS.434..765K,2016arXiv160205527F}.
Current data do not deliver images but require fitting to predefined
models for the images.  A whole range of models have been applied,
starting from simple geometric models to more complex physical models
\citep{2008Natur.455...78D,2011ApJ...738...38B,2009ApJ...706..497M,2010ApJ...717.1092D}.
The more complicated models nonetheless tend to predict a crescent
shaped silhouette of the black hole.  This motivated
\cite{2013MNRAS.434..765K} to use a simple geometric crescent model to
fit the data, and argued that the crescent is nothing but the
silhouette of the event horizon.

@@

\begin{figure}
% \centering
  \includegraphics[width=0.5\textwidth]{figures/cc_forward.eps}
\caption{\label{fig:cc_forward} Mock lightcurve fitted with the
  correct source type and caustic.  The upper panel shows the mock
  data points, and running through them is a seven-parameter best fit:
  these being the crescent parameters $(R_p,R_n,a,b)$ and additionally
  the start and end times and the overall normalisation.  (Ideal
  lightcurves for the same crescent parameters appear above in
  Figures~\ref{fig:lightcurve_gauss}, \ref{fig:lightcurve_disk},
  \ref{fig:lightcurve_crescent} and \ref{fig:char_points}.)  The curve
  has $\chi^2=243, P=0.32$ indicating a good fit.  The lower panel
  shows the posterior distributions for $r_{1/2}$ (solid histogram)
  and $R_n/R_p$ (dashed histogram).}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{figures/cc_backward.eps}
\caption{\label{fig:cc_backward} Like Figure~\ref{fig:cc_backward},
  except that the fit uses path~II whereas the mock data still come
  from path~I. The curve has $\chi^2=284, P=0.01$ indicating a
  marginally acceptable fit.}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{figures/gc_forward.eps}
\caption{\label{fig:gc_forward} Like Figure~\ref{fig:cc_backward}, but
  showing the best fit to a Gaussian source.  The histogram shows the
  posterior distribution of $r_{1/2}$ (there is no $R_n$).  It appears
  to show $r_{1/2}$ as accurately recovered, but is not to be trusted,
  because the fit has $\chi^2=344, P=3\times10^{-6}$ indicating
  rejection of the Gaussian source.  Looking closely, the curve is a
  little too shallow near $t=3$, and it is unable to fit the second
  sub-peak near $t=5$.}
\end{figure}
